Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-02 docs/ms.tex
Update ms.tex

The typical procedure of weak lensing analysis usually include ellipticity
measurement,shear inference,mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infere shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we set
up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
add on the true lensed ellipticity.We suppose there is a uniform shear
acting on one all the galaxies in sky patch,

>>>>

The typical procedure of weak lensing analysis usually include ellipticity
measurement,shear inference,mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infere shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we set
up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,
